TacticToe: Learning to Prove with Tactics

### 2018-03-19 tactictoe_jv.tex
Abstract

\begin{abstract}
We implement a tactical prover TacticToe on top of the HOL4 interactive theorem
prover. TacticToe learns from human proofs which mathematical method is
useful in a particular proof situation.
This knowledge is then used in a Monte Carlo tree search algorithm that
explores the most promising tactic-level proof paths.
On a single CPU, with a time limit of 60 seconds, TacticToe proves 66.4\% of
7164 theorems in HOL4's standard library whereas
Eprover solves 34.5\%. The success rate rises to 69.0\% by combining the
results of TacticToe and Eprover.
\end{abstract}

>>>>

\begin{abstract}
We implement a tactical prover TacticToe on top of the HOL4 interactive theorem
prover. TacticToe learns from human proofs which mathematical technique is
the most suitable in each proof situation.
This knowledge is then used by a Monte Carlo tree search algorithm to
explore the most promising tactic-level proof paths.
On a single CPU, with a time limit of 60 seconds, TacticToe proves 66.4\% of
7164 theorems in HOL4's standard library whereas
Eprover solves 34.5\%. The success rate rises to 69.0\% by combining the
results of TacticToe and Eprover.
\end{abstract}
